\newpage
\section{Introduction}
	\subsection{Purpose}
		This document represents the Project Plan Document.\\ It specifies the effort and cost estimation of the myTaxiService project, by using Function Points and COCOMO algorithmic techniques. Moreover, it is given an explanation of the organization of the resources and of the tasks needed, along with the list of all the risks it is possible to encounter.\\
		The intended audience of this document is the project stakeholders and the development team.
	\subsection{Definitions and abbreviations}
		\begin{itemize}
			\item \textbf{Definitions}
			\item[-] \textbf{User}: a person who requests a service from the system. It can be a visitor or a passenger.
			\item[-] \textbf{Visitor}: a person who is not registered in the application.
			\item[-] \textbf{Passenger}: a person who is registered in the application.
			\item[-] \textbf{Taxi driver}: a taxi driver who access the application with a specific ID.
			\item[-] \textbf{Request}: the request of a taxi in a certain area and position in the city made by a user.
			\item[-] \textbf{Reservation}: the reservation of a taxi in a certain area, place and time that can be made only by passengers.
	
			\item \textbf{Acronyms and abbreviations}
			\item[-] \textbf{RASD}: Requirement Analysis and Specification Document
			\item[-] \textbf{DD}: Design Document
			\item[-] \textbf{FP}: Function Points
			\item[-] \textbf{COCOMO}: COnstructive COst MOdel
			\item[-] \textbf{ILF}: Internal Logic Files
			\item[-] \textbf{EIF}: External Interface Files
			\item[-] \textbf{KSLOC}: Kilo Source Lines Of Code
			\item[-] \textbf{EAF}: Effort Adjustment Factor
		\end{itemize}
	
	\newpage
	\subsection{Reference documents}
		\begin{itemize}
			\item Project Description and Rules (\url{https://github.com/MichelaCattaneo/myTaxiService/blob/master/Project\%20Description\%20And\%20Rules.pdf})
			\item Requirements Analysis and Specification Document (\url{https://github.com/MichelaCattaneo/myTaxiService/blob/master/Deliveries/RASD_1.1.pdf})
			\item Design Document (\url{https://github.com/MichelaCattaneo/myTaxiService/blob/master/Deliveries/DD.pdf})
			\item Code Inspection Document(\url{https://github.com/MichelaCattaneo/myTaxiService/blob/master/Deliveries/CodeInspection.pdf})
			\item Integration Test Document (\url{https://github.com/MichelaCattaneo/myTaxiService/blob/master/Deliveries/ITPD.pdf})
		\end{itemize}